### 2013-10-30 src2/thesis.tex
update
p

Push arrays were invented by Koen Claessen and first implemented in Obsidian 
to provide more control over where computation takes place (which thread computes 
which element). Push arrays has since been experimented on by others and show up 
in Nikola~\citet{NIKOLAPUSH}, Feldspar and appear in StreamHS~\citet{FPCDSL}.

>>>>

Push arrays were invented by Koen Claessen and first implemented in Obsidian 
to provide more control over where computation takes place (which thread computes 
which element). Push arrays has since been experimented on by others and show up 
in Nikola~\citet{NIKOLAPUSH} and Feldspar. Push arrays appear in StreamHS~\citet{FPCDSL} 
and ~\citet{MOA} as part of a multi-dimensional array calculus in Standard ML.
